---
title: "Visualization using a wine data set"
author: "Kevin Greenberg"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r, include = FALSE}
library(tidyverse)
library(dplyr)
library(DT)
library(knitr)
library(ggmap)
library(ggalt)
library(leaflet)
library(shiny)
library(ggpubr)

```

```{r data_import, cache=TRUE, include = FALSE}
   wine <- read.csv(url("https://raw.githubusercontent.com/JackStat/PracticalDataScience/master/data/winemag-data-130k-v2.csv"))

```

### Introduction {#anchorP1}

We have a dataset of nearly 130,000 different wines with their ratings, price, tasters, country of origin, variety and much more. That is a lot of wine to look at so we are going to narrow it down to wines from one of my favorite places "Portugal."


```{r wine}
   WP <- filter(wine, country == 'Portugal')
dim(WP)
```

Using `dim(df)` we can see that there are 5691 different wines, and 92 varieties. If we put all 92 into a bar graph it's a little messy, so we are going to ignore the varieties that have a less than 20 wines in them. Now let's take a look at the different varieties of wine Portugal has to offer.



```{r fig.width=10,fig.height=5}

PV <- WP %>%
   group_by(variety) %>%
     summarise(count = n()) %>%
  filter(count > 20)

ggplot(PV, aes(x=factor(variety), y=count, fill = variety)) + 
  geom_bar(stat="identity") + 
  geom_text(aes(label=count, y = count), size=3) +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank() ,
        axis.ticks.x=element_blank()) +
  theme(legend.key.size = unit(0.2, "cm")) +
  guides(fill=guide_legend(ncol=2,byrow=TRUE)) +
  ggtitle("Varities of Wine in Portugal")
```
There's a lot of wines there. I could just show you a table if I used `kable(WP)`, but what's the fun in that, and it'd be a lot of scrolling. With `DT::datable(WP)` you can search anything in the table.

If you search 'Port' you will see there are 607 varieties of Port made in Portugal. We are going to focus on this specific variety of wine.


```{r fig.width=10,fig.height=5}
SumP <- WP %>%
  group_by(variety) %>%
  summarise(
    count = n(),
    Average_Price = mean(price), na.rm =TRUE,
    Average_Points = mean(points, na.rm = TRUE)
  )

SumP <- SumP[,-4]
SumP <- rename(SumP, c(`Variety of wine` = variety, `Count of Wineries that produce the variety` = count, `Average Price (US $)` = Average_Price, `Average Points` = Average_Points))


DT::datatable((SumP), 
              class = 'cell-border stripe', 
              caption = 'Table 1: All the of wine in Portugal, with the average price and points by variety.')


```

### Port Wine 

```{r fig.width=10,fig.height=5}
Port <- filter(WP, variety == 'Port') 
Port <- Port [, c(3,4,5,6,14)]
Port <- rename(Port, c('Description' = description, 'Type' = designation, 'Points' = points, 'Price (US $)' = price, 'Winery' = winery))

DT::datatable((Port), options = list(
  autoWidth = TRUE,
  columnDefs = list(list(width = '500px', targets = 1)),
  pageLength = 5),
  class = 'cell-border stripe',
caption = 'Table 2: This is a table of all the Port wine.')

```

### Price of Port by points

We see that Ports that received points from 80 to 95 in general have a similar price range, but when a port receives 95 plus points, then the price really jumps. 


```{r fig.width=10,fig.height=5}
ggplot(Port, aes(x = Points, y = `Price (US $)`)) +
geom_point(position = 'jitter', shape=42, size=10) +
  geom_smooth(method='lm',formula=y~x, se = FALSE) +
  theme_bw()+
  ggtitle("Price by Points of Port")
```

### Count of wineries making Port in Portugal

If we look at the Port by the winery we can tell there are 97 different wineries, by using `wine <- filter(wine, variety == 'Port') %>% group_by(winery) %>% summarise(count = n())`


Now it be great to be able to taste wines from all these different places, but let's narrow the Ports down to a few you can commonly purchase in the United States.



```{r fig.width=10,fig.height=5}
selectPorts <- filter(Port,grepl('Broad|Church|Dow|Ferr|Fonseca|do Noval|Warre|Taylor|Kopke|Sand', Winery)
             )
ggplot(selectPorts, aes(x=Winery, fill=Winery))+
  geom_bar(width = 1) +
  coord_polar(theta = "x") +
  theme_dark() 
 

```
As you can see Taylor Flagate and Kopke have the most Ports in this dataset.
Now Lets move away from the data and go look where these Ports come from.


### Location of a a few wineries in Portgual

```{r fig.width=10,fig.height=5}
leaflet() %>%
  setView(lng= -7.5441, lat = 41.17, zoom = 10) %>%
  addTiles() %>%
  addMarkers(lng =-7.554869499999995, lat = 41.1681615, popup = "Sandeman") %>%
addMarkers(lng =-7.5434, lat = 41.1873, popup = "Churchill's") %>%
  addMarkers(lng =-7.580222999999933, lat = 41.17443799999999, popup = "Taylor Fladgate") %>%      
  addMarkers(lng =-7.5957965999999715, lat = 41.15083540000001, popup = "Broadbent") 



```
Jump to the [Top](#anchorP1)




